Lentiptical galaxies and their ordinary black holes

### 2015-07-10 papers/lentiptical/lentiptical.tex
fri

\documentclass[preprint2]{emulateapj}

@@

\shorttitle{Lentiptical galaxies}
\shortauthors{Savorgnan \& Graham}

@@

\title{Lentiptical galaxies and their ordinary black holes}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%\author{C. D. Biemesderfer\altaffilmark{4,5}}
%\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
\email{gsavorgn@astro.swin.edu.au}

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
Lentiptical galaxies are an intermediate class of galaxies between elliptical  
and lenticular galaxies.
Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
Lentiptical galaxies have often been confused with lenticular galaxies and,
consequently, their bulge luminosities have been largely underestimated. 
This surprisingly common mistake has led to some wrong conclusions, 
such as the claim that a number of lentiptical galaxies are extreme outliers 
in the $M_{\rm BH} - M_{\rm *,sph}$ diagram, 
i.e. these galaxies host a central black hole whose mass, $M_{\rm BH}$, is abnormally large 
compared to expectations from their (underestimated) bulge stellar mass, $M_{\rm *,sph}$.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{keywords}

@@

\acknowledgments
luca cortese, peppo gavazzi, matteo fossati
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

@@

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

>>>>

\documentclass[12pt,preprint]{nature}

@@

@@

Title: Lentiptical galaxies \\
Authors: G. A. D. Savorgnan and A. W. Graham \\
Affiliation: Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia. \\

\begin{abstract}
Early-type galaxies are quiescent galaxies, with little or no star formation activity. 
The majority of early-type galaxies are made of two principal components: 
a spheroid (or bulge) of stars with random motion and a rapidly rotating stellar disk (1 krajnovic). 
The relative importance of these two components determines the morphological classification of early-type galaxies into two types: 
elliptical galaxies are spheroid-dominated systems, 
whereas lenticular galaxies are composed of a small bulge of stars encased in a larger stellar disk. 
When perfoming bulge/disk decomposition, 
the spheroidal component is typically described with a S\'ersic profile (2 sersic), 
while the disk is fit with an exponential function. 
Theoretically, the bulge-to-disk ratio, 
which describes the relative importance of the spheroidal component over the disk component, 
can assume any positive value. 
However, several studies have taken into account only bulge/disk decompositions 
in which the exponential function neatly dominates over the S\'ersic profile at large galaxy radii, 
and rejected those decompositions in which the exponential function remains ``embedded'' within the S\'ersic profile, 
considering such decompositions as unphysical.
Here we show that these rejected models correctly reproduce the kinematics of a class of early-type galaxies, 
that we name \emph{lentiptical}. 
Lentiptical galaxies have often been confused with lenticular galaxies and, 
consequently, their bulge luminosities have been largely underestimated. 
This surprisingly common mistake has led to some wrong conclusions, 
such as the claim that a number of lentiptical galaxies host a central black hole whose mass is abnormally large 
compared to expectations from its (underestimated) bulge luminosity.

Our results demonstrate that there is no bimodality in the distribution of the bulgetodisk
that the claimed bimodality is artificial

we show that the ell profile is enough to estabilish if the disk is embedded or not

%Lentiptical galaxies are an intermediate class of galaxies between elliptical  
%and lenticular galaxies.
%Lentipticals are early-type, bulge-dominated galaxies that feature a fast-rotating, 
%intermediate-scale disk of stars embedded within a slow-rotating spheroid of stars.
%Such spheroid dominates the light in the central region of the galaxy and also at large radii, 
%unlike lenticular galaxies, whose bulge is encased within a (more extended) large-scale disk. 
\end{abstract}

@@

luca cortese, peppo gavazzi, matteo fossati
%%
%%We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
%%doing the math in section~\ref{bozomath}.
%%More information on the AASTeX macros package is available \\ at
%%\url{http://www.aas.org/publications/aastex}.
%%For technical support, please write to
%%\email{aastex-help@aas.org}.
%%
%%%% To help institutions obtain information on the effectiveness of their
%%%% telescopes, the AAS Journals has created a group of keywords for telescope
%%%% facilities. A common set of keywords will make these types of searches
%%%% significantly easier and more accurate. In addition, they will also be
%%%% useful in linking papers together which utilize the same telescopes
%%%% within the framework of the National Virtual Observatory.
%%%% See the AASTeX Web site at http://aastex.aas.org/
%%%% for information on obtaining the facility keywords.
%%
%%%% After the acknowledgments section, use the following syntax and the
%%%% \facility{} macro to list the keywords of facilities used in the research
%%%% for the paper.  Each keyword will be checked against the master list during
%%%% copy editing.  Individual instruments or configurations can be provided 
%%%% in parentheses, after the keyword, but they will not be verified.
%%
%%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
%%
%%%% Appendix material should be preceded with a single \appendix command.
%%%% There should be a \section command for each appendix. Mark appendix
%%%% subsections with the same markup you use in the main body of the paper.
%%
%%%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%%%% The equation counter will reset when it encounters the \appendix
%%%% command and will number appendix equations (A1), (A2), etc.
%%
%%\appendix
%%
%%\section{Appendix material}
%%
%%Consider once again a task that computes profile parameters for a modified
%%Lorentzian of the form
%%\begin{equation}
%%I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
%%\end{equation}
%%where
%%\begin{mathletters}
%%\begin{displaymath}
%%d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
%%\end{displaymath}
%%\begin{equation}
%%d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
%%\end{array} \right) ^{2} +
%%\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
%%\end{equation}
%%\begin{eqnarray}
%%x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
%%y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
%%\end{eqnarray}
%%\end{mathletters}
%%
%%For completeness, here is one last equation.
%%\begin{equation}
%%e = mc^2
%%\end{equation}

@@

%\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
